Improving the Performance of Distributed Data Parallelism \\Over a Low Bandwidth

### 2023-01-04 paper/paper.tex
paper update

\begin{abstract}
There is no doubt that networking is a bottleneck when training neural networks across multiple nodes. Having a low bandwidth or a high delay in time it takes for data to be transferred between nodes can drastically increase training time of a neural network. It has become industry standard to use fast networking with bandwidths of up to 100Gbps this makes the requirements for training across multiple nodes very expensive. \\
2. Research methods\\
3. is viable
\end{abstract}
\tableofcontents
\newpage

@@

We plan to use 8bit quantization using both non-linear and block-wise techniques. non-linear quantization doesn't effect bandwidth it just helps to reduce variance. Block-wise allows us to decrease the gradients size by a factor of 4 but adds $\frac{p}{k}\times 256$ float16 numbers on top of the quatized gradients in order to undo the quantization where $p$ is the number of parameters and $k$ is the value that determines the number of block usually 2048 or 4096. For the example of vgg16 you decrease the graidents to around 110 MB in size but add an extra size of 8,000,000 32 bit floating points.

When using sparsification with quantization, sparsification occours before quantization and quantizaion only occours on the non zero grads.

@@

By doubling the batch size you should half the communication time as there half as many communication step taking place in an epoch. Whilest using a dynamic batch size it can take quite a long time before the batch size doubles as the it takes multiple epoch before the train error halfs.

>>>>

\begin{abstract}
There is no doubt that networking is a bottleneck when training neural networks across multiple GPUs and computers. Having a low bandwidth or a high latency can drastically increase training time of a neural network. In this paper we look at a variety of methods to reduce the effect of a low bandwidth including gradient sparsification, gradient quantization and a using a large batch size. We find ... COULDN'T FIND COMPUTER
\end{abstract}
\tableofcontents
\newpage

@@

We plan to use 8bit quantization using both non-linear and block-wise techniques. non-linear quantization doesn't effect bandwidth it just helps to reduce variance. Block-wise allows us to decrease the gradients size by a factor of 4 but adds $\frac{p}{k}\times 256$ float16 numbers on top of the quantized gradients in order to undo the quantization where $p$ is the number of parameters and $k$ is the value that determines the number of block usually 2048 or 4096. For the example of vgg16 you decrease the gradients to around 110 MB in size but add an extra size of 8,000,000 32 bit floating points.

When using sparsification with quantization, sparsification occurs before quantization and quantization only occurs on the non zero grads.

@@

By doubling the batch size you should half the communication time as there half as many communication step taking place in an epoch. Whilst using a dynamic batch size it can take quite a long time before the batch size doubles as the it takes multiple epoch before the train error halves.
